Potential of I/O-Aware Workflows in Climate and Weather

### 2020-02-19 paper.tex
Minor

The information Cylc uses to control a given workflow is the task dependency.
The scientists make the configuration about parallelism and data location in the script file that is executed for each specific task.
%Decisions about storage must take into consideration the system architecture and the relevance of heterogeneous infrastructure in which the workflow will run.

@@

We aim for achieving an automatic and dynamic mapping of I/O resources to workflows.
Once we have an automated decision about where the job will run and how the storage will be managed, scientists can then run their workflows on any system without further modification and even without previous knowledge about the system architecture.

@@

Note that the user may not be able to provide all required information.
This can be handled by assuming a default safe behavior.
For instance, in case of a missing data precision, data should be retained in original form.
Knowing the dimension or size a priori might be difficult for scientists, e.g., the log file size is unclear.
In this case, the user may insert relative information like small or big, reflecting that any information is better than no information at all.
In future, we will explore how to automatically infer the output volume from the input or by using monitoring.

@@

By monitoring I/O accesses, we can automatically draft such I/O descriptions on behalf of the user to simplify the specification.

All we need is to run one cycle of the specific workflow, considering that a workflow cycle is executed many times in climate and weather; this is a cheap approach.

>>>>

The information Cylc uses to control a given workflow is the task dependency.
The developers define, in a script file, for each task the parallelism settings and where the data is to be stored.
%Decisions about storage must take into consideration the system architecture and the relevance of heterogeneous infrastructure in which the workflow will run.

@@

We aim for achieving an automatic and dynamic mapping of I/O resources to workflows.
Once we have an automated decision about where the job will run and how the storage will be managed, scientists can then reuse their workflow specification on any system without further modification and even without previous knowledge about the system architecture.

@@

Note that the user may not be able to provide all required information.
This can be handled by assuming a default safe behavior.
For instance, in case of a missing data precision, data should be retained in original form.
Knowing the dimension or size a priori might be difficult for scientists, e.g., the log file size is unclear.
In this case, the user may insert relative information like small or big, reflecting that any information is better than no information at all.
In future, we will explore how to automatically infer the output volume from the input or by using monitoring.
By allowing to run using an empty I/O workflow specification and monitoring I/O accesses for one cycle, we can propose an I/O description to the user to simplify the specification.

@@
